Tabular Constraint Learning

### 2016-05-02 Paper/ECAI/tabular.tex
Added paragraph on group generation and provided some more details on subgroup assignment finder

\tias{Add paragraph on enforcement of group generation}

@@

\subsubsection{Subgroup satisfaction search}
$\findassignment(t,A,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that the corresponding constraint $t(G_1', ..., G_n')$ is satisfied.
For every \template~$t$ an implementation (declarative or imperative) needs to be provided that finds valid subgroups given the assignments.

>>>>

\samuel{TODO: correct code integer groups}\\
Consider the \ecrank{v_r}{v_x} constraint template, then both arguments must be of the same length.
Therefore, assignments containing groups of different length do not have to be considered.
Constraints of the \CSignature cannot always be enforced directly on a group but have to consider whether subgroups could satisfy them.
For example, the \CSignature requires $v_r$ to be integer.
If a numeric group is assigned to $v_r$ then some subgroups may have type float while other may be of type integer, therefore, this this group cannot be discarted.

@@

\subsubsection{Subgroup satisfaction search}
$\findassignment(t,A,C_{solutions})$ finds, for all assignments~$a = (G_1, ..., G_n)$ in $A$, the subgroups $G_i' \subseteq G_i$ such that the corresponding constraint $t(G_1', ..., G_n')$ is satisfied (i.e. the \CSignature and \CFunction of~$t$ are satisfied).
For every \template~$t$ an implementation (declarative or imperative) needs to be provided that, given an assignment, finds valid subgroups.
